---
title: "Fun with network graphs"
author: "Will Landau"
date: "July 25, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

The <a href="https://datastorm-open.github.io/visNetwork/">visNetwork</a> package is my new favorite tool for visualizing network graphs. It is customizable, flexible, and fun. All you need is a data frame of nodes and a data frame of edges. The interactive plot lets you zoom, pan, and drag with the mouse. Try it!

```{r intro}
library(visNetwork)
nodes <- data.frame(id = 1:3, label = 1:3)
edges <- data.frame(from = c(1,2), to = c(1,3))
visNetwork(nodes, edges, width = "100%")
```

<a href="https://datastorm-open.github.io/visNetwork/">visNetwork</a> is particularly handy when it comes to larger, more cumbersome graphs. As an example, let us plot the package dependency network of <a href="http://ggplot2.org/">ggplot2</a>. We can get an <a href="http://igraph.org/">igraph</a> object from <a href="https://cran.r-project.org/package=miniCRAN/vignettes/miniCRAN-dependency-graph.html">miniCRAN</a>, but the default static plot is dense.

```{r igraph}
library(miniCRAN)
igraph <- makeDepGraph("ggplot2")
plot(igraph)
```

<a href="https://datastorm-open.github.io/visNetwork">visNetwork</a> has a slick <a href="http://igraph.org/">igraph</a> API.

```{r visNetwork}
library(visNetwork)
network_data <- toVisNetworkData(igraph)
nodes <- network_data$nodes
edges <- network_data$edges
edges$arrows <- "to"
```

The interactivity and ordered layout make all the difference.

```{r plot}
library(magrittr)
visNetwork(nodes = nodes, edges = edges, width = "100%") %>%
  visHierarchicalLayout(direction = "LR") %>%
  visNodes(physics = FALSE) %>%
  visInteraction(navigationButtons = TRUE)
```
